Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-04-13 gtsummary_submission.tex

% adding table describing trial dataset
\input{tex_tables/tbl_trial_desc.tex}

@@

% adding table describing fns for customization
\input{tex_tables/tbl_modify.tex}

@@

The example below includes customization using both \pkg{gtsummary} and \pkg{gt} functions.
The \pkg{gtsummary} functions are utilized to bold p-values below a threshold, bold the variable labels,  update the column header, and add a spanning header.
Additional \pkg{gt} customization was utilized to add table captions and source notes.

@@

For example, using the theme for \textit{The Journal of the American Medical Association} (\textit{JAMA}), large p-values are rounded to two decimal places, confidence intervals are shown as \code{"lb to ub"} instead of \code{"lb, ub"}, and the confidence internal is displayed in the same column as the model coefficient.

>>>>

\newpage
% adding table describing trial dataset
\input{tex_tables/tbl_trial_desc.tex}

@@

\newpage
% adding table describing fns for customization
\input{tex_tables/tbl_modify.tex}

@@

The example below includes customization using both \pkg{gtsummary} and \pkg{gt} functions.
The \pkg{gtsummary} functions are utilized to bold the variable labels,  update the column headers, and add a spanning header.
Additional \pkg{gt} customization was utilized to add table captions and source notes.

@@

For example, using the theme for \textit{The Journal of the American Medical Association} (\textit{JAMA}), large p-values are rounded to two decimal places, confidence intervals are shown as \code{"lb to ub"} instead of \code{"lb, ub"}, and the confidence internal is displayed in the same column as the model coefficients.
